\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Michael Evdokimov} % Your name

\address{+7(915)329-1299 \\ \href{mailto:maevdokimov_1@edu.hse.ru}{maevdokimov\_1@edu.hse.ru}}  % Your phone number, email, linkedin, and (optional) website

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{Software Engineer, data-scientist, seeking an internship for computer science/business roles.}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor, 2nd-year Faculty of Computer Science}, HSE University \hfill {Expected 2022}\\

%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technical Skills & C++, Python development, Predicting high-frequency time series, \\ & a course in economics and minor in international business\\
\\
Soft Skills & Creativity, sociable, easily find contact with people, learn quickly\\
\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}

I have experience working in and managing several business and educational projects, like developing algorithms for MTS Music to determine the highlights in the song, almost ready-made backend and design, but the customer then stopped showing interest. Engaged in project presentation and backend development. Also, we developed a mobile app based on tracking the location of friends and making various events for those who are nearby, like Zenly. Personally, worked on the concept of the entire project and frontend and backend development on IOS. Experience in IOS development at Swift. Project presentation and pitching in them and others.

Lead the team in various hackathons, including the largest international hackathon in Russia - Hack.Moscow, winner of the main hackathon of Moscow Leaders of Digital Transformation 2020, etc. 

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Several projects and business idea.} I had a team-leading experience, working, and creating projects with my friends and classmates dedicated to developing programs for the HR Department, mobile applications.
\end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Cirrucular Activities} 
\begin{itemize}
    \item 	Surfing, tennis, travel and more.
\end{itemize}


\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Leadership} 
\begin{itemize}
    \item Creativity
    \item Have a positive attitude to all my colleagues
    \item Trustworthiness
    \item Always open to criticism and communication
\end{itemize}


\end{rSection}


\end{document}
